---
title: "Survey Methodology"
author: "SW"
date: Last updated on `r Sys.Date()`
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Survey Methodology

* Here is a sample of survey methodology: [Thematic Household Survey Report No. 84 - Explanatory Notes](https://stevenkhwun.github.io/testrepo/Survey_Methodology/THS84_Explanatory Notes.pdf)

* Key terms
  * [Coefficient of variation](https://en.wikipedia.org/wiki/Coefficient_of_variation)
  
  * [Standard deviation vs standard error](https://library.soton.ac.uk/variance-standard-deviation-and-standard-error#:~:text=Standard%20deviation%20is%20used%20to,using%20software%20than%20by%20hand.)

```{r}
# To calculate the variance and standard deviation of the above dataset in R, we can create
# a variable for the data and then calculate the variance and standard deviation with the 
# 'var' and 'sd' functions respectively:
dataset <- c(7, 12, 5, 18, 5, 9, 10, 9, 12, 8, 12, 16)
var(dataset)
sd(dataset)
```

```{r}
# To find the standard error, you can define your own function to be simply the standard
# deviation divided by the square root of n and apply that function to the dataset:
standard.error <- function(x) sd(x)/sqrt(length(x))
standard.error(dataset)
```

# Sampling Methods

## Simple Random Sample

A simple random sample is chosen by a process that selects a sample of $n$ objects from a population in such a way that each member of the population has the same probability of being selected, the selection of one member is independent of the selection of any other member, and every possible sample of a given size, $n$, has the same probability of selection.

## Sampling distribution

The population mean $\mu$, is a fixed (but unknown) number. We make inferences about this attribute by drawing a random sample from the population and computing the sample mean. For each sample we draw, there will be a different sample mean, and the sample mean can be regarded as a random variable with a probability distribution. The distribution of
possible sample means provides a basis for inferential statements about the sample.

### Definition

Consider a random sample selected from a population that is used to make an inference about some population characteristic, such as the population mean, $\mu$, using a sample statistic, such as the sample mean, $\bar{x}$. We realize that every sample has different observed values and, hence, different sample means. The sampling distribution of the sample mean is the probability distribution of the sample means obtained from all possible samples of the same number of observations drawn from the population.

